Mealtime conversations between parents and their 2-year-old children in five cultural contexts

### 2023-11-30 manuscript/paper.Rmd
update preprint

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "manuel_bohn@eva.mpg.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal Analysis
      - Visualization
      - Writing – original draft
      - Writing – review & editing
  - name          : "Wilson Filipe da Silva Vieira"
    affiliation   : "2"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Marta Giner Torréns"
    affiliation   : "3"
    role:
      - Investigation
      - Conceptualization
      - Methodology
      - Writing – review & editing
  - name          : "Joscha Kärtner"
    affiliation   : "3"
    role:
      - Investigation
      - Conceptualization
      - Methodology
      - Writing – review & editing
  - name          : "Shoji Itakura"
    affiliation   : "4"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Lília Cavalcante"
    affiliation   : "5"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Daniel Haun"
    affiliation   : "2"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Moritz Köster"
    affiliation   : "6,*"
    role:
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing
  - name          : "Patricia Kanngiesser"
    affiliation   : "7,*"
    role:
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

affiliation:
  - id            : "1"
    institution   : "Institute of Psychology, Leuphana University Lüneburg, Lüneburg, Germany"
  - id            : "2"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "3"
    institution   : "Department of Psychology, University of Münster, Münster, Germany"
  - id            : "4"
    institution   : "Center for Baby Science, Doshisha University, Kyoto, Japan"
  - id            : "5"
    institution   : "Graduate Program in Theory and Research of Behavior, Federal University of Pará, Belém, Brazil"
  - id            : "6"
    institution   : "Institute of Psychology, University of Regensburg, Regensburg, Germany"
  - id            : "7"
    institution   : "School of Psychology, University of Plymouth, Plymouth, UK"
  - id            : "*"
    institution   : "joint senior authors"

@@

abstract: |
  Children all over the world learn language, yet, the contexts in which they do so varies substantially. This variation needs to be systematically quantified to build robust and generalizable theories of language acquisition. We compared communicative interactions between parents and their two-year-old children (N = 99 families) during mealtime across five cultural settings (Brazil, Ecuador, Argentina, Germany, Japan) and coded the amount of talk and gestures as well as their conversational embedding (interlocutors, function, themes). We found a comparable pattern of communicative interactions across cultural settings, which were modified in ways that are consistent with local norms and values. These results suggest that children encounter similarly structured communicative environments across diverse cultural contexts and will inform theories of language learning.

keywords          : "Language acquisition, Communication, Gesture, Cross-cultural psychology, Parent-child interaction"
wordcount         : "8454"

@@

classoption       : "man"
output            : papaja::apa6_docx
---

@@

```{r}
# cluster1 <- data%>%
#   mutate(key = family)%>%
#   select(-country,family)%>%
#   group_by(key)%>%
#   summarise(no_questions = sum(speech_act=="q", na.rm = T),
#             no_assertions = sum(speech_act=="a", na.rm = T),
#             no_imperatives = sum(speech_act=="i", na.rm = T),
#             utterances = sum(no_assertions,no_imperatives,no_questions),
#             Questions = no_questions/utterances,
#             Assertions = no_assertions/utterances,
#             Imperatives = no_imperatives/utterances,
#             Gestures = sum(grepl("gesture", speaker), na.rm = T),
#             recipient_father = sum(recipient=="f", na.rm = T),
#             recipient_mother = sum(recipient=="m", na.rm = T),
#             recipient_child = sum(recipient=="c", na.rm = T),
#             Themes = length(unique(theme)),
#             Rounds = mean(as.numeric(round), na.rm = T))%>%
#   select(-c(no_questions,no_assertions,no_imperatives,utterances, recipient_father, recipient_mother, recipient_child))%>%ungroup()
# 
# cluster2 <- data%>%
#   filter(!grepl("gesture",speaker))%>%
#   mutate(key = family)%>%
#   group_by(key, speaker)%>%
#   #make props here
#   summarise(talk = sum(duration))%>%
#   spread(speaker, talk)%>%
#   mutate(`Father speaker` = father/(father+mother+child),
#          `Mother speaker` = mother/(father+mother+child),
#          `Child speaker` = child/(father+mother+child),
#          `Non-talk` = silence)%>%
#   ungroup()%>%
#   select(-c(father,mother,child,silence))
# 
# cluster3 <- data%>%
#   filter(!grepl("gesture",speaker),
#          speaker != "silence")%>%
#   group_by(family, theme)%>%
#   summarise(no_speakers = n_distinct(speaker))%>%
#   mutate(key = family)%>%
#   group_by(key)%>%
#   summarise(`Speakers per theme` = mean(no_speakers))%>%
#   ungroup()
# 
# 
# cluster <- cluster1 %>%left_join(cluster2)%>%left_join(cluster3)
# 
# cluster_data <- cluster%>%mutate_if(is.numeric, scale)%>% remove_rownames %>% column_to_rownames(var="key")%>%filter(!is.na(`Non-talk`))
# 
# fviz_nbclust(cluster_data, kmeans, method = "wss")
# 
# fviz_nbclust(cluster_data, kmeans, method = "silhouette")
# 
# final <- kmeans(cluster_data, 2, nstart = 25)
# 
# res.hc <- eclust(cluster_data, "hclust", k = 2)
# 
# countries <- data%>%
#   distinct(family, .keep_all = T)%>%
#   select(family, country)
# 
# cols <- recode(countries$country[res.hc$order], Argentina = "#4477AA", Germany = "#88CCEE", Japan = "#117733", Brazil = "#DDCC77", Ecuador = "#CC6677")
# 
# clus <- fviz_dend(res.hc,
#           rect = TRUE,
#           type = "rectangle",
#           rect_border = F,
#           cex = 0.75,
#           label_cols = cols)+
#   theme_void()+
#   scale_color_manual(values=rev(natparks.pals("Yellowstone",2)))+
#   theme(title = element_blank())

@@

```{r}
# profil <- as_tibble(final$centers, rownames = "Cluster")%>%
#   pivot_longer( cols = c(2:12), names_to = "dimension", values_to = "value") %>%
#   mutate(dimension = factor(dimension, levels = rev(c("Non-talk","Father speaker","Mother speaker","Child speaker","Speakers per theme", "Rounds","Themes","Questions","Assertions","Imperatives","Gestures"))),
#          Cluster = factor(Cluster))%>%
#   arrange(dimension)%>%
#   ggplot(., aes(x = value, y = dimension, col = Cluster))+
#   geom_point()+
#   geom_path(aes(group = Cluster))+
#   xlim(-1.5, 1.5)+
#   labs(y = "", x = "Cluster mean (standardized)")+
#   #scale_y_discrete(limits=rev)+
#   scale_color_manual(values=c("#0067A2", "#DFCB91"), name = "Cluster", labels = c("1","2"))+
#   theme_bw()+
#   theme(legend.position = c(0.1,0.8), legend.background = element_blank())+
#   guides(colour = guide_legend(reverse=F))
```

>>>>

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Institute of Psychology in Education, Leuphana University Lüneburg, Universitätsallee 1, 21335 Lüneburg, Germany"
    email         : "manuel.bohn@leuphana.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal Analysis
      - Visualization
      - Writing – original draft
      - Writing – review & editing
  - name          : "Wilson Filipe da Silva Vieira"
    affiliation   : "2"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Marta Giner Torréns"
    affiliation   : "3"
    role:
      - Investigation
      - Conceptualization
      - Methodology
      - Writing – review & editing
  - name          : "Joscha Kärtner"
    affiliation   : "3"
    role:
      - Investigation
      - Conceptualization
      - Methodology
      - Writing – review & editing
  - name          : "Shoji Itakura"
    affiliation   : "4"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Lília Cavalcante"
    affiliation   : "5"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Daniel Haun"
    affiliation   : "2"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Moritz Köster"
    affiliation   : "6,*"
    role:
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing
  - name          : "Patricia Kanngiesser"
    affiliation   : "7,*"
    role:
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

affiliation:
  - id            : "1"
    institution   : "Institute of Psychology in Education, Leuphana University Lüneburg, Lüneburg, Germany"
  - id            : "2"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "3"
    institution   : "Department of Psychology, University of Münster, Münster, Germany"
  - id            : "4"
    institution   : "Center for Baby Science, Doshisha University, Kyoto, Japan"
  - id            : "5"
    institution   : "Graduate Program in Theory and Research of Behavior, Federal University of Pará, Belém, Brazil"
  - id            : "6"
    institution   : "Institute of Psychology, University of Regensburg, Regensburg, Germany"
  - id            : "7"
    institution   : "School of Psychology, University of Plymouth, Plymouth, UK"
  - id            : "*"
    institution   : "joint senior authors"

@@

abstract: |
  Children all over the world learn language, yet, the contexts in which they do so vary substantially. This variation needs to be systematically quantified to build robust and generalizable theories of language acquisition. We compared communicative interactions between parents and their two-year-old children (N = 99 families) during mealtime across five cultural settings (Brazil, Ecuador, Argentina, Germany, Japan) and coded the amount of talk and gestures as well as their conversational embedding (interlocutors, function, themes). We found a comparable pattern of communicative interactions across cultural settings, which were modified in ways that are consistent with local norms and values. These results suggest that children encounter similarly structured communicative environments across diverse cultural contexts and will inform theories of language learning.

keywords          : "Language acquisition, Communication, Gesture, Cross-cultural psychology, Parent-child interaction"
wordcount         : "8451"

@@

classoption       : "man"
output            : papaja::apa6_pdf
---

@@

```{r}
# cluster1 <- data%>%
#   mutate(key = family)%>%
#   select(-country,family)%>%
#   group_by(key)%>%
#   summarise(no_questions = sum(speech_act=="q", na.rm = T),
#             no_assertions = sum(speech_act=="a", na.rm = T),
#             no_imperatives = sum(speech_act=="i", na.rm = T),
#             utterances = sum(no_assertions,no_imperatives,no_questions),
#             Questions = no_questions/utterances,
#             Assertions = no_assertions/utterances,
#             Imperatives = no_imperatives/utterances,
#             Gestures = sum(grepl("gesture", speaker), na.rm = T),
#             recipient_father = sum(recipient=="f", na.rm = T),
#             recipient_mother = sum(recipient=="m", na.rm = T),
#             recipient_child = sum(recipient=="c", na.rm = T),
#             Themes = length(unique(theme)),
#             Utterances = mean(as.numeric(round), na.rm = T))%>%
#   select(-c(no_questions,no_assertions,no_imperatives,utterances, recipient_father, recipient_mother, recipient_child))%>%ungroup()
# 
# cluster2 <- data%>%
#   filter(!grepl("gesture",speaker))%>%
#   mutate(key = family)%>%
#   group_by(key, speaker)%>%
#   #make props here
#   summarise(talk = sum(duration))%>%
#   spread(speaker, talk)%>%
#   mutate(`Father speaker` = father/(father+mother+child),
#          `Mother speaker` = mother/(father+mother+child),
#          `Child speaker` = child/(father+mother+child),
#          `Non-talk` = silence)%>%
#   ungroup()%>%
#   select(-c(father,mother,child,silence))
# 
# cluster3 <- data%>%
#   filter(!grepl("gesture",speaker),
#          speaker != "silence")%>%
#   group_by(family, theme)%>%
#   summarise(no_speakers = n_distinct(speaker))%>%
#   mutate(key = family)%>%
#   group_by(key)%>%
#   summarise(`Speakers per theme` = mean(no_speakers))%>%
#   ungroup()
# 
# 
# cluster <- cluster1 %>%left_join(cluster2)%>%left_join(cluster3)
# 
# cluster_data <- cluster%>%mutate_if(is.numeric, scale)%>% remove_rownames %>% column_to_rownames(var="key")%>%filter(!is.na(`Non-talk`))
# 
# fviz_nbclust(cluster_data, kmeans, method = "wss")
# 
# fviz_nbclust(cluster_data, kmeans, method = "silhouette")
# 
# final <- kmeans(cluster_data, 2, nstart = 25)
# 
# res.hc <- eclust(cluster_data, "hclust", k = 2)
# 
# countries <- data%>%
#   distinct(family, .keep_all = T)%>%
#   select(family, country)
# 
# cols <- recode(countries$country[res.hc$order], Argentina = "#4477AA", Germany = "#88CCEE", Japan = "#117733", Brazil = "#DDCC77", Ecuador = "#CC6677")
# 
# clus <- fviz_dend(res.hc,
#           rect = TRUE,
#           type = "rectangle",
#           rect_border = F,
#           cex = 0.75,
#           label_cols = cols)+
#   theme_void()+
#   scale_color_manual(values=rev(natparks.pals("Yellowstone",2)))+
#   theme(title = element_blank())

@@

```{r}
# profil <- as_tibble(final$centers, rownames = "Cluster")%>%
#   pivot_longer( cols = c(2:12), names_to = "dimension", values_to = "value") %>%
#   mutate(dimension = factor(dimension, levels = rev(c("Non-talk","Father speaker","Mother speaker","Child speaker","Speakers per theme", "Utterances","Themes","Questions","Assertions","Imperatives","Gestures"))),
#          Cluster = factor(Cluster))%>%
#   arrange(dimension)%>%
#   ggplot(., aes(x = value, y = dimension, col = Cluster))+
#   geom_point()+
#   geom_path(aes(group = Cluster))+
#   xlim(-1.5, 1.5)+
#   labs(y = "", x = "Cluster mean (standardized)")+
#   #scale_y_discrete(limits=rev)+
#   scale_color_manual(values=c("#0067A2", "#DFCB91"), name = "Cluster", labels = c("1","2"))+
#   theme_bw()+
#   theme(legend.position = c(0.1,0.8), legend.background = element_blank())+
#   guides(colour = guide_legend(reverse=F))
```
